---
title: "Query 1"
author: "Dan Fanelli"
date: "4/11/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Query 1

select 
    langPeopGeo.PeopleID3, peops.PeopName, 
    langPeopGeo.ROG3, countries.Ctry, 
    langPeopGeo.ROL3, langs.Language,
    peopGeoRel.RLG3, rlg.PrimaryReligion, peopGeoRel.PercentAdherents, peopGeoRel.PercentEvangelical, peopGeoRel.PercentPracticing,
    peopGeo.PopulationPercentUN, peopGeo.PopulationRounded
from 
    tblLnkPEOtoGEO peopGeo,
    tbllnkLNGtoPEOGEO langPeopGeo, 
    tblLnkPEOtoGEOReligions peopGeoRel,
    tblPEO3PeopleGroups peops,
    tblGEO3Countries countries,
    tblLNG3Languages langs,
    tblRLG3Religions rlg
where peopGeo.PeopleID3 = langPeopGeo.PeopleID3
and peopGeo.ROG3 = langPeopGeo.ROG3
and langPeopGeo.PeopleID3 = peops.PeopleID3
and langPeopGeo.ROG3 = countries.ROG3
and langPeopGeo.ROL3 = langs.ROL3
and peopGeoRel.PeopleID3 = langPeopGeo.PeopleID3
and peopGeoRel.ROG3 = langPeopGeo.ROG3
and peopGeoRel.RLG3 = rlg.RLG3
and peopGeoRel.ROG3 = 'US'
order by peopGeo.PopulationPercentUN desc

```{r cars}
library(knitr)
library(sqldf)

df <- read.csv(file="../../data/query_1/results.csv", header=TRUE, sep=",")
kable(df)
```

